A tutorial on the model-dependent analysis of neutron and X-ray reflectometry

### 2020-08-27 refl_maths/paper.tex
stylistic changes following wojteks comments

\section{Overfitting}

When defining a model care must be taken to balance the complexity of the model with the fit to the data.
By using too few parameters we risk that important structural features are not covered by the model and that fit to the data is worse than optimal. 
However over-paramaterizng the model may lead to over-fitting to the data and therefore deriving false conclusions about the measured sample. 
The latter issue is particularly problematic for reflectometry data for which information content/density is typically low. 
Different strategies have been used to address over-fitting in reflectometry. Typically a "rule of thumb" of choosing the most simple model that enables a description
of the data has been applied. Even though such method is easy to apply it requires prior knowledge about the sample (e.g. from different experimental technique) and making assumption about information content in the data i.e. do we have enough information to support the model. 
The information content can in principle be quantified directly from the data as has been widely demonstrated for small-angle scattering data, which also typically suffers from limited structural information (\cite{Larsen_2018} and references therein) or by validating model given the data. 
The example of latter approach uses Bayesian model selection framework to compare models with different numbers of parameters to determine which  offers the maximum information without over-fitting \cite{hughes_model_selection_2019, McCluskey_bayesian_model_selection_2020}. While this approach provides rigours framework for finding "optimal" model it is also important to note that it depends on the prior probabilities chosen for each of the parameters.
The problem of finding an optimal model can also be inverted to another task of acquiring "optimal" data that can support given model. Treece et al. developed a method based on Bayesian statistics and information theory that quantifies information gain from reflectometry experiments with the purpose of guiding experimental design \cite{Treece_2019}. 
Regardless of the method used to mitigate over-fitting, we are limited to information covered by the data. To overcome this limitation one can supplement data with the information from other techniques. This can be done by constraining model parameters with values obtained from other experiments or by simultaneously fitting model against multiple experimental data sets. These can be other reflectometry measurements (e.g. from contrast variation) or from different technique (e.g. combination of X-ray and neutron reflectometry data). This can however be challenging because various data may differently contribute to information content and proper reweighing needs to be done. Bayesian statistics may be alleviate these limitations, however proper frameworks needs to be established.

>>>>

\section{Over-fitting}

When defining a model care must be taken to balance the complexity of the model with the fit to the data.
By using too few parameters we risk that important structural features are not covered by the model and that fit to the data is sub-optimal. 
However over-parameterising the model may lead to over-fitting to the data and therefore deriving false conclusions about the measured sample. 
The latter issue is particularly problematic for reflectometry data, for which information content/density is typically low.

Different strategies have been used to address over-fitting in reflectometry. 
Typically a ``rule of thumb'' of choosing the most simple model that enables a description of the data has been applied. 
Even though such method is easy to apply it requires prior knowledge about the sample, e.g. from different experimental technique, and making assumption about information content in the data, i.e. do we have enough information to support the model. 
The information content can in principle be quantified directly from the data as has been widely demonstrated for small-angle scattering data, which also typically suffers from limited structural information \cite{Larsen_2018} or by validating model given the data. 
The example of the latter approach uses Bayesian model selection framework to compare models with different numbers of parameters to determine which offers the maximum information without over-fitting \cite{hughes_model_selection_2019, mccluskey_general_2020}. 
While this approach provides rigorous framework for finding an ``optimal'' model it is also important to note that it depends on the prior probabilities chosen for each of the parameters.
The problem of finding an optimal model can also be inverted to another task of acquiring ``optimal'' data that can support given model. 
Treece et al. \cite{Treece_2019} developed a method based on Bayesian statistics and information theory that quantifies information gain from reflectometry experiments with the purpose of guiding experimental design.

Regardless of the method used to mitigate over-fitting, we are limited to information covered by the data. 
To overcome this limitation one can supplement data with the information from other techniques. 
This can be done by constraining model parameters with values obtained from other experiments or by simultaneously fitting model against multiple experimental data sets. 
These can be other reflectometry measurements (e.g. from contrast variation) or from different technique (e.g. combination of X-ray and neutron reflectometry data). 
This can however be challenging because various data may differently contribute to the information content and proper reweighing needs to be performed. 
Bayesian statistics may be alleviate these limitations, however proper frameworks need to be established.
